The Lipid Interactome Repository

### 2025-03-25 IndividualStudies/AT_2025.qmd
editing from Frank's suggestions, removing CNET
putting NAPE on the index
polishing dag page a little

---
title: "Thomas et al. 2025"
subtitle: "Trifunctional lipid derivatives: PE’s mitochondrial interactome"
format: 
  html:
    embed-resources: false
standalone: false
---
<!-- Data overview
Two lipid probes, PA and PE for a single cell line
 -->

@@

![](/IndividualStudies/GO_plots/PE-PA_AT_2025_CC-CNETplot.png)

@@

![](/IndividualStudies/GO_plots/PE-PA_AT_2025_MF-CNETplot.png)

@@

![](/IndividualStudies/GO_plots/PE-PA_AT_2025_BP-CNETplot.png)
:::

>>>>

---
title: "Thomas et al. 2025"
subtitle: "Trifunctional lipid derivatives: PE’s mitochondrial interactome"
date: 2024-12-26
format: 
  html:
    embed-resources: false
standalone: false
---
<!-- Data overview
Two lipid probes, PA and PE for a single cell line
 -->

@@

@@

@@

### 2025-03-25 IndividualStudies/DCC_2025.qmd
polishing dag page a little

---
title: "Chiu et al. 2025"
subtitle: "Photoaffinity Labeling Reveals a Role for the Unusual Triply Acylated Phospholipid N-Acylphosphatidylethanolamine in Lactate Homeostasis"
format: 
  html:
    embed-resources: false
standalone: false
---

>>>>

---
title: "Chiu et al. 2025"
subtitle: "Photoaffinity Labeling Reveals a Role for the Unusual Triply Acylated Phospholipid N-Acylphosphatidylethanolamine in Lactate Homeostasis"
date: 2025-03-06
format: 
  html:
    embed-resources: false
standalone: false
---

### 2025-03-25 IndividualStudies/DH_2017.qmd
putting NAPE on the index
polishing dag page a little

---
title: "Höglinger et al. 2017"
subtitle: "Trifunctional lipid probes for comprehensive studies of single lipid species in living cells"
format:
  html:
    embed-resources: false
standalone: false
---
<!-- R setup, reading data tables, wrangling data -->
```{r setup, echo=FALSE, include=FALSE, warning=FALSE}

@@

>>>>

---
title: "Höglinger et al. 2017"
subtitle: "Trifunctional lipid probes for comprehensive studies of single lipid species in living cells"
date: 2017-02-14
format:
  html:
    embed-resources: false
standalone: false
---
<!-- R setup, reading data tables, wrangling data -->
```{r setup, echo=FALSE, include=FALSE, warning=FALSE}

@@

## Data exploration

### 2025-03-25 IndividualStudies/RM_2021.qmd
putting NAPE on the index
polishing dag page a little

---
title: "Muller et al. 2021"
subtitle: "Synthesis and Cellular Labeling of Multifunctional Phosphatidylinositol *Bis*- and *Tris*phosphate Derivatives"
format: 
  html:
    embed-resources: false
standalone: false
---

>>>>

---
title: "Muller et al. 2021"
subtitle: "Synthesis and Cellular Labeling of Multifunctional Phosphatidylinositol *Bis*- and *Tris*phosphate Derivatives"
date: 2021-06-01
format: 
  html:
    embed-resources: false
standalone: false
---

### 2025-03-25 IndividualStudies/SF_2024.qmd
polishing dag page a little

---
title: "Farley et al. 2024"
subtitle: "Trifunctional Sphinganine: A New Tool to Dissect Sphingolipid Function"
format: 
  html:
    embed-resources: false
standalone: false
---

>>>>

---
title: "Farley et al. 2024"
subtitle: "Trifunctional Sphinganine: A New Tool to Dissect Sphingolipid Function"
date: 2024-02-16
format: 
  html:
    embed-resources: false
standalone: false
---

### 2025-03-25 IndividualStudies/SF_2024_B.qmd
editing from Frank's suggestions, removing CNET
polishing dag page a little

---
title: "Farley et al. 2024 B"
subtitle: "Trifunctional fatty acid derivatives: the impact of diazirine placement"
format: 
  html:
    embed-resources: false
standalone: false
---

@@

![](/IndividualStudies/GO_plots/8-3FA-1-10FA_SF_2024_CC-CNETplot.png)

>>>>

---
title: "Farley et al. 2024 B"
subtitle: "Trifunctional fatty acid derivatives: the impact of diazirine placement"
date: 2024-05-25
format: 
  html:
    embed-resources: false
standalone: false
---

@@

### 2025-03-25 StudyInformation_includes/AT_2025_include.qmd
polishing dag page a little

<a href="/LipidProbe/Phosphatidylethanolamine.qmd" class="hover-preview">Trifunctional Phosphatidylethanolamine</a>
<span class="hover-image">
  <img src="/LipidProbe/Structures/TF_PE.png" alt="PPhosphatidylethanolamine" />
</span>

>>>>

<a href="/LipidProbe/Phosphatidylethanolamine.qmd" class="hover-preview">Trifunctional Phosphatidylethanolamine</a>
<span class="hover-image">
  <img src="/LipidProbe/Structures/TF_PE.png" alt="Phosphatidylethanolamine" />
</span>

### 2025-03-25 StudyInformation_includes/DH_2017_include.qmd
polishing dag page a little

[Trifunctional Sphingosine](/LipidProbe/Sphingosine.qmd)

[Trifunctional Diacylglycerol](/LipidProbe/Diacylglycerol.qmd)

[Trifunctional 8-3 Fatty acid](/LipidProbe/8-3_FattyAcid.qmd)

>>>>

<a href="/LipidProbe/Sphingosine.qmd" class="hover-preview">Trifunctional Sphingosine</a>
<span class="hover-image">
  <img src="Structures/TF_Sphingosine.png" alt="Trifunctional Sphingosine" />
</span>

<a href="/LipidProbe/Diacylglycerol.qmd" class="hover-preview">Trifunctional Diacylglycerol</a>
<span class="hover-image">
  <img src="Structures/TF_DAG.png" alt="Trifunctional Diacylglycerol" />
</span>

<a href="/LipidProbe/8-3_FattyAcid.qmd" class="hover-preview">Trifunctional 8-3 Fatty Acid</a>
<span class="hover-image">
  <img src="Structures/TF_8-3_fatty_acid.png" alt="Trifunctional 8-3 Fatty Acid" />
</span>
